SSA based global code motion of identical computations

### 2017-04-17 acmart-pacmpl-template.tex
fixes

\def \GCC {GCC}
\def \LLVM {LLVM}
\def \SESE {SESE}
\def \CFG {CFG}
\def \SSA {SSA}
\def \MemorySSA {MemorySSA}
\def \PRE {PRE}
\def \GVN {GVN}
\def \LLVMTestSuite {\LLVM{} test-suite}

@@

\begin{verbatim}
// Compute merge set top-down in breadth first order.
bool constructMergeSet_1(BFSList B, JEdges JE, DomLevel DL)
repeat = False
// List of visited edges
Visited V
for n in B do
  for e in (all incoming edges to n) do
    if (e is in JE && e not in V) then
      V(e) = true
      Let snode = Source Node of e
      Let tnode = Target Node of e
      Let tmp = snode
      Let lnode = NULL
      while (DL(tmp) ≥ DL(tnode)) do
        Merge(tmp) = Merge(tmp) U Merge(tnode) U {tnode}
        lnode = tmp
        tmp = dom-parent(tmp)
      end while
      repeat = still_inconsistent(lnode, JE, Merge)
    end if
  end for
end while
return repeat

@@

\begin{verbatim}
// Return true if the merge set of source node of
// a visited J-edge (incoming edge of lnode) is not
// the subset of the merge set of lnode.
bool still_inconsistent(Node lnode, JEdges JE, Visited V, MergeSet M)
   for (all incoming edges to lnode) do
     Let e = Incoming edge
     if (e is in JE && e in V) then
       Let snode = Source Node of e
       if (M(snode)!(Subset) M(lnode)) then
         return true
       end if
     end if
   end for
return false
\end{verbatim}

@@

\section{Experimental Evaluation}
\label{sec:experimental-results}
% Experimental results: Register spills, compile time, run time. compile-time comparison w.r.t. gcc
We ran \LLVMTestSuite{} (trunk:d87471f8) with the patch (trunk:86940146). All
the experiments were conducted on x86\_64 Ubuntu-Linux machine and at -Ofast
optimization level.  The results for code-hoisting are listed in
Table~\ref{tab:hoist-results}. The table lists the number of scalars, loads,
stores and calls hoisted as well as removed. For each category, the number of
instructions removed is greater or equal to the number of instructions hoisted
because each hoisting is performed only when at least one identical computation
is found.

@@

Other static metrics are listed in Table~\ref{tab:static-results}. Here we can
see that except for rematerializing defs for splitting, which has an overhead of ~2\%, all
other parameters have less than 1\% overhead. This is to explain why the performance does not
go down with our implementation (and cost-model) of code hoisting pass.

>>>>

\def \GCC {GCC}
\def \LLVM {LLVM}
\def \SESE {SESE}
\def \CFG {CFG}
\def \SSA {SSA}
\def \MemorySSA {MemorySSA}
\def \PRE {PRE}
\def \GVN {GVN}
\def \LLVMTestSuite {\LLVM{} test-suite}
\def \SPEC {SPEC Cpu2006}

@@

\begin{verbatim}
// Return true if the merge set of source node of
// a visited J-edge (incoming edge of lnode) is not
// the subset of the merge set of lnode.
bool still_inconsistent(Node lnode, JEdges JE, Visited V, MergeSet M)
   for (all incoming edges to lnode) do
     Let e = Incoming edge
     if (e is in JE && e in V) then
       Let snode = Source Node of e
       if (M(snode) is not a subset of M(lnode)) then
         return true
       end if
     end if
   end for
return false

// Compute merge set top-down in breadth first order.
bool constructMergeSet_1(BFSList B, JEdges JE, DomLevel DL)
repeat = False
// List of visited edges
Visited V
for n in B do
  for e in (all incoming edges to n) do
    if (e is in JE && e not in V) then
      V(e) = true
      Let snode = Source Node of e
      Let tnode = Target Node of e
      Let tmp = snode
      Let lnode = NULL
      while (DL(tmp) ≥ DL(tnode)) do
        Merge(tmp) = Merge(tmp) U Merge(tnode) U {tnode}
        lnode = tmp
        tmp = dom-parent(tmp)
      end while
      repeat = still_inconsistent(lnode, JE, Merge)
    end if
  end for
end while
return repeat

@@

@@

\section{Experimental Evaluation}
\label{sec:experimental-results}
% Experimental results: Register spills, compile time, run time. compile-time comparison w.r.t. gcc
We ran \SPEC{} with the patch. All
the experiments were conducted on x86\_64 Ubuntu-Linux machine and at -Ofast
optimization level.  The results for code-hoisting are listed in
Table~\ref{tab:code-motion-metric}. The table lists the number of scalars, loads,
stores and calls hoisted as well as removed. For each category, the number of
instructions removed is greater or equal to the number of instructions hoisted
because each hoisting is performed only when at least one identical computation
is found.

@@

Other static metrics are listed in Table~\ref{tab:stats} and in Table~\ref{tab:code-motion-metric}.
Here we can
see that except for rematerializing defs for splitting, which has an overhead of ~2\%, all
other parameters have less than 1\% overhead. This is to explain why the performance does not
go down with our implementation (and cost-model) of code hoisting pass.
